Offshore Indices of Abundance for <br/> Blue Crabs

### 2020-01-05 2019_edits/R/offshore_analyses/IOA_report.Rmd

#packages
library(MASS)
library(here)
library(tidyverse)
library(knitr)
library(emmeans)
library(gridExtra)
library(broom)
library(statmod)
library(rnaturalearth)
library(sf)
conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")

@@

```{r}
# Read in data
#seamap <- read_csv(here("data_processed/gsmfc_processed", "seamap_cpue_2019.csv"),
seamap <- read_csv(here("data/offshore", "seamap_cpue_2019.csv"),
                   guess_max = 1e6, 
                   col_types = cols())

@@

year_plot_1
#ggsave(plot =  year_plot_1, here("figures", "yearly_catch.png"), dpi = 600)

@@

year_plot_2
#ggsave(plot = year_plot_2, here("figures", "yearly_occurrence.png"), dpi = 600)

@@

```{r}
gridExtra::grid.arrange(
  grobs = list(year_plot_1, year_plot_2),
  nrow = 1)
```

@@

```{r}
#Assign Stat Zone from NMFS grid
#szones <- read_sf(here("GIS_objects",  "NMFS_Fishing_Grids_GOM_2013", "NMFS_Fishing_Grids_GOM_2013.shp"), crs = 4326)
szones <- read_sf(here("data/gis_files","NMFS_Fishing_Grids_GOM_2013.shp"), crs = 4326)

@@

szones_plot_1 
#ggsave(plot = szones_plot_1, here("figures", "statzones_catch.png"), dpi = 600)

@@

szones_plot_2
#ggsave(plot = szones_plot_2, here("figures", "statzones_occurrence.png"), dpi = 600)
```

@@

```{r}
gridExtra::grid.arrange(
  grobs = list(szones_plot_1, szones_plot_2),
  nrow = 1)
```

@@

#Output seamap analysis file
write_csv(seamap, here::here("data/offshore", "seamap_cpue_2019_analysis.csv"), 
          col_names = TRUE)

@@

region_plot_1 
#ggsave(plot = region_plot_1, here("figures", "regions_catch.png"), dpi = 600)
```

@@

region_plot_2
#ggsave(plot = region_plot_2, here("figures", "regions_occurrence.png"), dpi = 600)

@@

```{r}
gridExtra::grid.arrange(
  grobs = list(region_plot_1, region_plot_2),
  nrow = 1)
```

@@

gridExtra::grid.arrange(
  grobs = list(rs_plot_1 + theme(legend.position = "none"), rs_plot_2),
  nrow = 1)

@@

season_summary%>% select(Survey_Year, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
#knitr::kable(season_summary)
```

@@

season_plot_1 
#ggsave(plot =  year_plot_1, here("figures", "yearly_catch.png"), dpi = 600)

@@

```{r}
gridExtra::grid.arrange(
  grobs = list(season_plot_1 + theme(legend.position = "none"), season_plot_2),
  nrow = 1)
```

@@

```{r, message = FALSE, warning = FALSE, comment = NA, fig.height=8}
super_plot_tall <- grid.arrange(
  grobs = list(year_plot_1, year_plot_2+ ylab(""),
               season_plot_1, season_plot_2+ ylab(""),
               szones_plot_1, szones_plot_2+ ylab("")), 
  nrow = 3)
super_plot_tall
```

@@

super_plot_wide
```

>>>>

#packages
library(MASS)
library(here)
library(tidyverse)
library(knitr)
library(emmeans)
library(gridExtra)
library(patchwork)
library(broom)
library(statmod)
library(rnaturalearth)
library(sf)
conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")

@@

```{r}
# Read in data
#seamap <- read_csv(here("data_processed/gsmfc_processed", "seamap_cpue_2019.csv"),
#seamap <- read_csv(here("data/offshore", "seamap_cpue_2019.csv"),
seamap <- read_csv("~/Dropbox/SEAMAP_2019/data/offshore/seamap_cpue_2019.csv",
                   guess_max = 1e6, 
                   col_types = cols())

@@

year_plot_1
#ggsave(plot =  year_plot_1, here("2019_edits/figures", "yearly_catch.png"), dpi = 600)

@@

year_plot_2
#ggsave(plot = year_plot_2, here("2019_edits/figures", "yearly_occurrence.png"), dpi = 600)

@@

```{r}
year_plot_1 + year_plot_2
```

@@

```{r}
#Assign Stat Zone from NMFS grid
#szones <- read_sf(here("GIS_objects",  "NMFS_Fishing_Grids_GOM_2013", "NMFS_Fishing_Grids_GOM_2013.shp"), crs = 4326)
szones <- read_sf("~/Dropbox/SEAMAP_2019/data/gis_files/NMFS_Fishing_Grids_GOM_2013.shp", crs = 4326)

@@

szones_plot_1 
#ggsave(plot = szones_plot_1, here("2019_edits/figures", "statzones_catch.png"), dpi = 600)

@@

szones_plot_2
#ggsave(plot = szones_plot_2, here("2019_edits/figures", "statzones_occurrence.png"), dpi = 600)
```

@@

```{r}
szones_plot_1 + szones_plot_2
```

@@

#Output seamap analysis file
write_csv(seamap, 
          "~/Dropbox/SEAMAP_2019/data/offshore/seamap_cpue_2019_analysis.csv", 
          #here::here("data/offshore", "seamap_cpue_2019_analysis.csv"), 
          col_names = TRUE)

@@

region_plot_1 
#ggsave(plot = region_plot_1, here("2019_edits/figures", "regions_catch.png"), dpi = 600)
```

@@

region_plot_2
#ggsave(plot = region_plot_2, here("2019_edits/figures", "regions_occurrence.png"), dpi = 600)

@@

```{r}
region_plot_1 + region_plot_2
```

@@

rs_plot_1 + theme(legend.position = "none") + rs_plot_2

@@

season_summary %>% select(Survey_Year, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
#knitr::kable(season_summary)
```

@@

season_plot_1 
#ggsave(plot =  year_plot_1, here("2019_edits/figures", "yearly_catch.png"), dpi = 600)

@@

```{r}
season_plot_1 + theme(legend.position = "none") + season_plot_2
```

@@

```{r, message = FALSE, warning = FALSE, comment = NA, fig.height=8}
super_plot_tall <- grid.arrange(
  grobs = list(year_plot_1, year_plot_2+ ylab(""),
               season_plot_1, season_plot_2+ ylab(""),
               szones_plot_1, szones_plot_2+ ylab("")), 
  nrow = 3)
#super_plot_tall
```

@@

#super_plot_wide
```
